Notes about Spin and TR Symmetry

### 2016-10-30 Notes of Bernvig's Book/sections/Ch4 TR symmetry/Notes about TR symmetry.tex
Minor Modifications

>>>>

        \begin{lemma}
            For time reversal symmetric electron bands, its Berry
            phase is always $0$. Hence, the Hall conductance is also
            zero.
        \end{lemma}
        \begin{proof}
            Consider the Berry field strength:
            $$F_{ij}(\vb{k}) = \braket{\partial_i n(\vb{k})|\partial_j
            n(\vb{k})} - (i \leftrightarrow j) $$

            The time reversed state $T\ket{n(\vb{k})}
            =\ket{n^*(-\vb{k})}$, since $T$ flips $\vb{k}$ and is
            antiunitary. So in the time reversed state the Berry field
            strength is:
            $$F'_{ij}(\vb{k}) = \braket{\partial_i n^*(-\vb{k})|\partial_j
            n^*(-\vb{k})} - (i \leftrightarrow j) $$
            Notice that $\braket{n^*|m^*} = \braket{m|n}$, as can be
            seen if we use the position space wave function. Then we
            have
            $$F'_{ij}(\vb{k}) = -F_{ij}(-\vb{k})$$
            Also, the system is time reversal symmetric, so
            \begin{align}
                F_{ij}(\vb{k}) = F'_{ij}(\vb{k}) = -F_{ij}(-\vb{k})
            \end{align}
            Hence $F_{ij}$ is an odd function and its integration over
            the whole BZ is $0$.
        \end{proof}
